% rubber path /home/matt/Downloads/moderncv
\documentclass[12pt,letter,roman]{moderncv}
\moderncvstyle{custom}
\moderncvcolor{black}
\nopagenumbers

\usepackage[scale=0.85]{geometry}
\usepackage{charter}

\firstname{Matthew}
\familyname{Pfefferle}
\address{4606 Bridle Path Lane}{Dublin, Ohio 43017}
\mobile{+1(614)464-7146}
\email{matthew.pfefferle@gmail.com}
%% \social[linkedin][http://www.linkedin.com/in/mpfefferle/]
%% \social[github][https://github.com/pfeff]
%% \social[github][https://github.com/mpfefferle]

\begin{document}
\makecvtitle

\section{Summary of Qualifications}

Senior software and DevOps engineer. Demonstrated success automating software
delivery and infrastructure in both large and small organizations. 10 years
experience in Dev and Ops.

\subsection{Technical Expertise}

\cvitem{DevOps \& Automation} { Ansible, Chef, Puppet, Jenkins, Leiningen, Maven, Git }
\cvitem{Cloud} { SoftLayer, Bluemix, Docker, Vagrant, Packer, Heroku }
\cvitem{Programming Languages} { Clojure, Ruby/Rails, Python, Java, C\#, C++, Bash, JavaScript, PHP, SQL }
\cvitem{Web Infrastructure} { Apache, Nginx, ActiveMQ, Nagios, Zabbix, PagerDuty }
\cvitem{Security} { Authentication and Access Control, Attack Mitigation (web applications) }
\cvitem{Web Services} { SOAP, WSDL, REST, SAML/SSO }
\cvitem{Server Platforms} { Linux (RedHat, CentOS, Ubuntu), JBoss 5-7 }
\cvitem{Development Methodologies} { Scrum, Continuous Delivery, Waterfall }
\cvitem{Networking} { JunOS, Netconf, SLAX }

\section{Experience}

%% \setlength{\parskip}{0.25em}
\cventry{June 2014 -- Present}{Software DevOps Engineer}{IBM, Business
Analytics}{Dublin,
  OH}{}{}

Automate software delivery for business analytics applications on IBM public
and private clouds. DevOps subject matter expert.

\begin{itemize}

    \item[$\bullet$] Upgrading system infrastructure for analytics software and introducing configuration management using Chef.

    \item[$\bullet$] Implement continuous delivery pipeline to enable rapid development of new analytics applications.

    \item[$\bullet$] Ensure system reliability through monitoring and test automation.

\end{itemize}

\cventry{November 2012 -- May 2014}{Professional Services
  Consultant}{Juniper Networks}{Columbus, OH}{}{}

Implement automation solutions and "NetOps" for Juniper customers.

\begin{itemize}

  \item[$\bullet$] Implemented a Ruby on Rails based network automation
      solution to rapidly provision 1000+ switches and firewalls for a major
      restaurant chain.  The solution enabled a multi-million dollar hardware
      sale.

  \item[$\bullet$] Implemented tools to automate upgrades of business critical
      core routers for a major wireless provider in Australia.

\end{itemize}

\vspace{0.5em}
\cventry{July 2011 -- November 2012}{Software Engineer 4}{Juniper Networks}{Columbus, OH}{}{}

Responsible for feature development, bug fixes, and project automation on the
Junos Pulse Mobile Security Gateway.  The cloud-based, multi-tenant, enterprise
management server manages security and usage policies on major
smartphone platforms including iOS, Android, BlackBerry, Symbian, and Windows
Mobile.

\begin{itemize}

    \item[$\bullet$] Implemented continuous deployment using Jenkins, Maven, and RPM.

    \item[$\bullet$] Upgraded development platform from JBoss 5 to JBoss AS 7 in order to
        take advantage of improved performance, security, and manageability.
        Leveraged the JBoss management API in order to automate installation,
        configuration, and deployment of the system.

    \item[$\bullet$] Implemented Single Sign-On using the SAML SSO protocol and the OpenSAML
        library.

\end{itemize}

\vspace{0.5em}
\cventry{July 2010 -- July 2011}{Software Engineering Associate Manager}{Juniper
Networks}{Columbus, OH}{}{}

Managed integration of acquired SMobile technologies following the
acquisition by Juniper Networks in July 2010.  Maintained product
development and release cadence during integration.

\vspace{0.5em}
\cventry{November 2008 -- July 2010}{Director of Architecture}{SMobile Systems
}{Columbus, OH}{}{}

Responsible for the design and delivery of the company's enterprise management
server product.

\begin{itemize}

    \item[$\bullet$] Managed new feature development while migrating the system from a
        legacy PHP implementation to an Enterprise Java implementation.

    \item[$\bullet$] Integrated billing and distribution with third-party vendors.

    \item[$\bullet$] Simplified product registration eliminating the need for redundant
        versions of the application.

    \item[$\bullet$] Wrote technical documentation for internal and external use.

\end{itemize}

\vspace{0.5em}
\cventry{May 2007 -- November 2008}{.NET Applications Developer}{Exceptional
Innovation}{Westerville, OH}{}{}

Extended the Life|ware home automation platform and related tooling.

\begin{itemize}
    \item[$\bullet$] Extended Life|ware's home automation scripting engine
    \item[$\bullet$] Developed new releases of the Life|ware configuration tool, Visual Project
    \item[$\bullet$] Developed feature enhancements within Life|ware's service oriented architecture.
\end{itemize}

\vspace{0.5em}
\cventry{July 2004 -- May 2007}{Vice President of Engineering}{SMobile
Systems}{Columbus, OH} {}{}

Managed the design, implementation, and release of all of SMobile's software
products.

\begin{itemize}

    \item[$\bullet$] Led the implementation of an integrated security product for Series
        60 2nd and 3rd editions through Symbian signing and deployment to a tier
        1 mobile network operator in Europe.

    \item[$\bullet$] Designed a flexible product architecture enabling rapid customization
        for new clients and shifting requirements.

    \item[$\bullet$] Extracted and continuously refined functional specifications from vague
        and sometimes ambiguous business requirements.

\end{itemize}

\vspace{0.5em}
\cventry{July 2004 -- May 2007}{Software Engineer}{SMobile Systems}{Columbus, OH}{}{}

Responsible for the design, implementation, and customer acceptance of all
SMobile products running on SymbianOS.  Routinely delivered timely and fully
functional releases.

\begin{itemize}

    \item[$\bullet$] Implemented, maintained, and customized numerous commercial security
        products including an anti-virus, an SMS and call filter, and an
        encryption tool for all major Symbian platforms.

    \item[$\bullet$] Automated build and deployment procedures to ensure project
        consistency among multiple developers, reducing integration delays by
        75\%.

    \item[$\bullet$] Applied object-oriented analysis and design techniques to create class
        libraries re-used throughout the organization.

    \item[$\bullet$] Supervised offshore development efforts.

\end{itemize}

\section{Education}

\cventry{2004}{B.S. Electrical and Computer Engineering}{The Ohio State University}{Columbus, OH}{}{}

\end{document}

