% rubber path /home/matt/Downloads/moderncv
\documentclass[12pt,letter,sans]{moderncv}
\moderncvstyle{custom}
\moderncvcolor{blue}
\nopagenumbers

\usepackage[scale=0.85]{geometry}

\firstname{Matthew}
\familyname{Pfefferle}
\address{4606 Bridle Path Ln}{Dublin, Ohio 43017}
\mobile{+1(614)464-7146}
\email{matthew.pfefferle@gmail.com}

\begin{document}
\makecvtitle

\section{Summary}

I am a software engineer with a proven track record in mobile, cloud, and
enterprise application development. As a manager and as a contributor I have
had many successful software product releases in areas serving large
telecommunication service providers. My ability to adapt to changing business
and technical environments has allowed me to deliver high quality software
products given shifting requirements and tight deadlines and resources.

\subsection{Specialties}

Software Engineering, Smart Phones, Internet and Web Technology, Open Source, Linux, Java

\subsection{Programming Languages}

Java, Ruby, Python, C\#

\section{Experience}

\cventry{July 2011 -- Present}{Software Engineer 4}{Juniper Networks}{}{}{}

As a software engineer at Juniper, I was responsible for feature development,
bug fixes, and project automation on the Junos Pulse Mobile Security Gateway.
The product is a cloud-based, multi-tenant, enterprise management server
responsible for managing security and usage policies on major smartphone
platforms including iOS, Android, BlackBerry, Symbian, and Windows Mobile.

My contributions in this role following integration of legacy SMobile technology
included:

\begin{itemize}

    \item A project automation system to implement continuous deployment.
        Based on the open source Jenkins continuous integration platform and the
        maven build tool, I implemented one-click and no-click processes capable
        of building, verifying, and deploying the application.
        The project included implementing a custom Maven plugin.

    \item
        Upgrading our development platform from JBoss 5 to JBoss AS 7 in order
        to take advantage of improved performance, security, and manageability.
        I was able to leverage the JBoss management API in order to automate installati
        on, configuration, and deployment of the system.

    \item
        Implementing Single Sign-On using the SAML SSO protocol and the OpenSAML
        library

\end{itemize}

\cventry{July 2010 -- July 2011}{Software Engineering Associate Manager}{Juniper
Networks}{}{}{}

Following the acquisition of SMobile Systems by Juniper Networks in July
2010, I was responsible for managing the integration of server technologies
and development into existing Juniper Processes.

\begin{itemize}
    \item
        Migrating legacy SMobile tools including defect tracking, source control,
        and release management tools into their Juniper equivalents.
    \item
        Training Juniper team members on the use and architecture of SMobile technology.
    \item
        Maintaining release cadence so that we could continue to deliver SMobile
        technology under the new Juniper brand.
\end{itemize}

\cventry{November 2008 -- July 2010}{Directory of Architecture}{SMobile Systems}{
}{}{}

As director of Architecture at SMobile Systems, I was responsible for the
design and delivery of the company's enterprise management server product.
In this role, I was able to manage new feature development while migrating
the system from a legacy PHP implementation to an Enterprise Java implementatio
n.

\cventry{May 2007 -- November 2008}{.NET Applications Developer}{Exceptional
Innovation}{}{}{}

I extended Life|ware's home automation scripting engine; developed new releases
of the Life| ware configuration tool, Visual Project; and developed feature
enhancements within Life|ware's service oriented architecture.

\cventry{July 2004 -- May 2007}{Vice President of Engineering}{SMobile Systems}{}
{}{}

Managed the design, implementation, and release of all of SMobile’s software
products.

\begin{itemize}

    \item Lead the implementation of an integrated security product for Series
        60 2nd and 3rd editions through Symbian signing and deployment to a tier
        1 mobile network operator in Europe.
    \item Designed a flexible product architecture enabling rapid customization
        for new clients and shifting requirements.
    \item Extracted and continuously refined functional specifications from vague
        and sometimes ambiguous business requirements.
\end{itemize}

\cventry{July 2004 -- May 2007}{Software Engineer}{SMobile Systems}{}{}{}

Responsible for the design, implementation, and customer acceptance of all
SMobile products running on SymbianOS.  Routinely delivered timely and fully
functional releases.

\begin{itemize}
    \item
        Implemented, maintained, and customized numerous commercial security products
        including an Anti-Virus, an SMS and call filter, and an encryption tool
        for all major Symbian platforms.
    \item
        Automated build and deployment procedures to ensure project consistency
        among multiple developers, reducing integration delays by 75%.
    \item

        Applied Object Oriented analysis and design techniques to create class
        libraries re-used throughout the organization
\end{itemize}

\section{Education}

\cventry{2000 -- 2004}{B.S. Electrical and Computer Engineering}{The Ohio State University}{Columbus, OH}{GPA 3.13}{}

\end{document}

