% rubber path /home/matt/Downloads/moderncv
\documentclass[12pt,letter,sans]{moderncv}
\moderncvstyle{custom}
\moderncvcolor{black}
\nopagenumbers

\usepackage[scale=0.85]{geometry}

\firstname{Matthew}
\familyname{Pfefferle}
\address{4606 Bridle Path Ln}{Dublin, Ohio 43017}
\mobile{+1(614)464-7146}
\email{matthew.pfefferle@gmail.com}

\begin{document}
\makecvtitle

\section{Summary of Qualifications}

Principal designer of the original Pulse Mobile Security Gateway with intimate
knowledge of its internals, capabilities, and limitations.  Experience
customizing the MSG and designing/documenting APIs for large carrier customers.
Supervised internal and outsourced teams developing MSS and MSG functionality.

\subsection{Technical Expertise}

\begin{description}
    \item[Web Services] SOAP, WSDL, REST, SAML/SSO
    \item[Programming Languages] Java, JSP, Ruby, PHP, Python, Bash, JavaScript, XML
    \item[Frameworks] Spring, Hibernate, Rails
    \item[Server Platforms] Linux (RedHat, CentOS, Ubuntu), JBoss 5, JBoss AS 7, Jenkins
    \item[Mobile Platforms] SymbianOS
    \item[Operations] Continuous Deployment, Jenkins, Capistrano
    \item[Development Methodologies] Scrum, NPI, CDM
\end{description}

\section{Experience}

\cventry{July 2011 -- Present}{Software Engineer 4}{Juniper Networks}{}{}{}

Responsible for feature development, bug fixes, and project automation on the
Junos Pulse Mobile Security Gateway.  The cloud-based, multi-tenant, enterprise
management server manages security and usage policies on major
smartphone platforms including iOS, Android, BlackBerry, Symbian, and Windows
Mobile.

\begin{itemize}

    \item Implemented continuous deployment using Jenkins, Maven, and RPM.

    \item Upgraded development platform from JBoss 5 to JBoss AS 7 in order to
        take advantage of improved performance, security, and manageability.
        Leveraged the JBoss management API in order to automate installation,
        configuration, and deployment of the system.

    \item Implemented Single Sign-On using the SAML SSO protocol and the OpenSAML
        library

\end{itemize}

\cventry{July 2010 -- July 2011}{Software Engineering Associate Manager}{Juniper
Networks}{}{}{}

Managed the integration of SMobile server technologies and development into
existing Juniper processes, following the acquisition of SMobile Systems by
Juniper Networks in July 2010.

\begin{itemize}

    \item Migrated legacy SMobile tools including defect tracking, source
        control, and release management tools into their Juniper equivalents.

    \item Trained Juniper team members on the use and architecture of SMobile technology.

    \item Maintained release cadence in order to continue delivery of SMobile
        technology during integration.

    \item Wrote functional specifications for proposed new functionality.

\end{itemize}

\cventry{November 2008 -- July 2010}{Director of Architecture}{SMobile Systems
}{Columbus, OH}{}{A security products vendor specializing in smartphone security.
Acquired by Juniper Networks, July 2010}

Responsible for the design and delivery of the company's enterprise management
server product.

\begin{itemize}

    \item Managed new feature development while migrating the system from a
        legacy PHP implementation to an Enterprise Java implementation.

    \item Integrated billing and distribution with third-party vendors.

    \item Simplified product registration eliminating the need for redundant
        versions of the application.

    \item Wrote technical documentation for internal and external use.

\end{itemize}

\cventry{May 2007 -- November 2008}{.NET Applications Developer}{Exceptional
Innovation}{Westerville, OH}{}{}

Extended the Life|ware home automation platform and related tooling.

\begin{itemize}
    \item Extended Life|ware's home automation scripting engine
    \item Developed new releases of the Life|ware configuration tool, Visual Project
    \item Developed feature enhancements within Life|ware's service oriented architecture.
\end{itemize}

\cventry{July 2004 -- May 2007}{Vice President of Engineering}{SMobile
Systems}{Columbus, OH} {}{}

Managed the design, implementation, and release of all of SMobile’s software
products.

\begin{itemize}

    \item Lead the implementation of an integrated security product for Series
        60 2nd and 3rd editions through Symbian signing and deployment to a tier
        1 mobile network operator in Europe.

    \item Designed a flexible product architecture enabling rapid customization
        for new clients and shifting requirements.

    \item Extracted and continuously refined functional specifications from vague
        and sometimes ambiguous business requirements.

\end{itemize}

\cventry{July 2004 -- May 2007}{Software Engineer}{SMobile Systems}{}{}{}

Responsible for the design, implementation, and customer acceptance of all
SMobile products running on SymbianOS.  Routinely delivered timely and fully
functional releases.

\begin{itemize}

    \item Implemented, maintained, and customized numerous commercial security
        products including an Anti-Virus, an SMS and call filter, and an
        encryption tool for all major Symbian platforms.

    \item Automated build and deployment procedures to ensure project
        consistency among multiple developers, reducing integration delays by
        75%.

    \item Applied object-oriented analysis and design techniques to create class
        libraries re-used throughout the organization.

    \item Supervised offshore development efforts.

\end{itemize}

\section{Education}

\cventry{2000 -- 2004}{B.S. Electrical and Computer Engineering}{The Ohio State University}{Columbus, OH}{GPA 3.13}{}

\end{document}

